Value-Suppressing Uncertainty Maps

### 2017-03-25 paper/template.tex
Pre-size manipulating hex maps.

Despite the acknowledged importance of uncertainty in understanding data, explicit representation of uncertainty often missing from visualizations~\cite{boukhelifa2009uncertainty}. This is partially due to the complexity of uncertainty as a concept. In typologies from Thomson et al~\cite{thomson2005typology} and Buttenfield \& Beard~\cite{buttenfield1994graphical}, the authors note that many, occasionally contradictory, concepts can fall under the category of ``uncertainty,'' including data quality, sampling error, credibility, and provenance. This complicates

@@

\emph{Superposition}, or the overlay of glyphs representing uncertainty on top of a data map, is another common strategy.  Ware's~\cite{ware2009quantitative} \emph{textons} are an example of this strategy: monochrome glyphs that can encode an ordinal variable, or a binned quantitative variable. Greithe et al.~\cite{griethe2006visualization} and MacEachren~\cite{maceachren1992visualizing,maceachren1998visualizing} present other examples of this technique, including overlaid grids with ``fuzzy'' lines to indicate uncertainty, or overlaid treemaps with coarser and coarser resolution in uncertain regions. Costs to this approach include obscuring the underlying datamap (which can cause uncertainty information to dominate the display~\cite{brodlie2012review}), potential visual interactions (for instance, simultaneous contrast effects) that can impair the legibility of glyphs, and the necessity of performing spatial binning in order to ensure that there are a discrete number of uncertainty glyphs. How this binning is performed can introduce undesirable artifacts on the resulting visualization, and suppress important signals, or highlight spurious ones \cite{battersby2016shapes}.

@@

>>>>

Despite the acknowledged importance of uncertainty in understanding data, explicit representations of uncertainty are often missing from visualizations~\cite{boukhelifa2009uncertainty}. This is partially due to the complexity of uncertainty as a concept. In typologies from Thomson et al~\cite{thomson2005typology} and Buttenfield \& Beard~\cite{buttenfield1994graphical}, the authors note that many, occasionally contradictory, concepts can fall under the category of ``uncertainty,'' including data quality, sampling error, credibility, and provenance.

@@

\emph{Superposition}, or the overlay of glyphs representing uncertainty on top of a data map, is another common strategy. Error bars are a common example of this strategy: a mark indicating measurement error is superimposed atop a mark representing a point value. Ware's~\cite{ware2009quantitative} \emph{textons} are an example of this strategy applied to thematic maps: monochrome glyphs that can encode an ordinal variable, or a binned quantitative variable. Greithe et al.~\cite{griethe2006visualization} and MacEachren~\cite{maceachren1992visualizing,maceachren1998visualizing} present other examples of superimposed uncertainty in thematic maps, including overlaid grids with ``fuzzy'' lines to indicate uncertainty, or overlaid treemaps with coarser and coarser resolution in uncertain regions. Costs to this approach include obscuring the underlying datamap (which can cause uncertainty information to dominate the display~\cite{brodlie2012review}), potential visual interactions (for instance, simultaneous contrast effects) that can impair the legibility of glyphs, and the necessity of performing spatial binning in order to ensure that there are a discrete number of uncertainty glyphs. How this binning is performed can introduce undesirable artifacts on the resulting visualization, and suppress important signals, or highlight spurious ones \cite{battersby2016shapes}.

@@

\subsection{}
